Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-03-01 paper/main.tex
Cite properly

\documentclass[english,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage{babel}
\usepackage[section]{placeins}
\usepackage{flafter}
\usepackage{comment}
\usepackage{breakurl}
\usepackage{svg}
\usepackage[labelfont=bf,font=small]{caption}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm,includeheadfoot]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
%\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
%\setlength{\headheight}{40pt}
%\lhead{\textsc{\scidatalogo}}
\usepackage[comma,super,sort&compress]{natbib}

@@

\section*{Plan}

\noindent Generally
\begin{itemize}
    \item https://gin.g-node.org/; upload; datacite.yml; readme; reserve \&
        cite DOI in data availability section
\end{itemize}

\noindent Supplemental Material
\begin{itemize}
    \item introductory sentences (e.g. "To test...") and concluding statements
\end{itemize}

@@

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI and annotation data, analysis scripts to generate the results as well
as results are available in the gin repository,
\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}, accessible as Datalad (RRID:SCR\_003931) datasets.

>>>>

\documentclass[english,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage{babel}
\usepackage[section]{placeins}
\usepackage{flafter}
\usepackage{comment}
\usepackage{breakurl}
\usepackage{svg}
\usepackage[labelfont=bf,font=small]{caption}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm,includeheadfoot]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
%\setlength{\headheight}{40pt}
%\lhead{\textsc{\scidatalogo}}
\usepackage[comma,super,sort&compress]{natbib}

@@

@@

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI data, annotations, analysis scripts to generate the results, and
results as Datalad \citep{datalad} datasets, published to or linked from the
GIN repository
\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignedment pending). 
Unthresholded $Z$-maps of all contrasts
can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
%
